Untitled

### 2021-03-09 ms/manuscript.Rmd
Update MS
- add links for reviewers to data and code

Samples were collected in the field and stored in plastic bags with a small amount of water to keep them fresh during transport to the lab.
For sporophytes, 8 individuals (one individual = single whole frond including a \circa{ }2 cm section of rhizome) were used per treatment, and all individuals for each species came from a single population.
We did not attempt to differentiate genotypes between fronds in species with long-creeping rhizomes, which often form clonal mats; hence, in some cases, individuals may be genetically identical ramets.
All experiments were initiated within 48 h of collection.
Pre-treatment maximum photochemical yield of photosystem II (F~v~/F~m~) [@Kitajima1975] was measured in fresh plants after a 10 min period of dark-adaptation using a portable mini-PAM fluorometer (Walz Gmbh, Effeltrich, Germany).
Any samples with pre-treatment F~v~/F~m~ < 0.4 were excluded from analysis, as typical values of F~v~/F~m~ in healthy plants tend to be \circa{ }0.8 [@Bjorkman1987].
Samples were then transferred to desiccation chambers containing saturated salts at three different desiccation intensities or a control treatment with moist tissues (100 % RH), and water withheld for either a short (2 d) or long (15 d) interval [@Testo2013].
Conditions inside the desiccation chambers were monitored during the experiment using Track-It RH/Temp dataloggers (Monarch Instrument, Amherst, NH) logging every 10 min (2012 field season for species other than *Callistopteris apiifolia*) or Hobo ProV2 dataloggers logging every 5 min (2012 *Callistopteris apiifolia*, 2013, 2014 field seasons).
The desiccation chambers were kept in an air-conditioned room. 
Temperature inside the chambers was mean `mean(filmy_dt_chamber$temp) %>% round(1)` ± SD `r sd(filmy_dt_chamber$temp) %>% round(2)` °C (\figs `r s_figure_num("chamber")`).
Salts used for desiccation and their corresponding mean water potentials and approximate relative humidity and VPD are as follows: LiCl (-282 MPa, 18 % RH, 2.45 kPa), Mg(NO~3~)~2~ (-86 MPa, 58 % RH, 1.25 kPa), and NaCl (-38 MPa, 80 % RH, 0.60 kPa).
Following the desiccation treatment, plants were rewetted by wrapping them in wet tissues using water from a local stream.
Plants were allowed to rehydrate, and F~v~/F~m~ was again measured at 0.5 h, 24 h, and 48 h following rewetting.
Ability to recover from desiccation was quantified by comparing pre- and post-treatment F~v~/F~m~ [@WatkinsJr.2007c].

@@

Rapid light response curves were constructed for each species by measuring photosynthetic yield at gradually increasing levels of photosynthetically active actinic light (400 nm to 700 nm) with the Light Curve function of the mini-PAM portable chlorophyll fluorometer (Walz Gmbh, Effeltrich, Germany) as described by the manufacturer.
Briefly, the maximum yield (F~m~) was first measured in the absence of actinic light.
Next, plants were equilibrated to the actinic light for 30 s, and photosynthetic yield (∆F/F~m~) measured with a 0.8 s saturating pulse.
This was repeated for each photosynthetic photon flux density (PPFD) level, up to ca.
500 µmol·m^-2^·s^-1^.
Response curves were fitted using the equation $y = A(1 - e^{-kx})$, where *y* is relative electron transport rate of photosystem II (RETR), *x* is photosynthetic photon flux density (PPFD), *A* is the asymptote of the curve, and *k* is a slope parameter; outliers at high PPFD likely to distort the curve were discarded [@Proctor2012].
The PPFD at 95 % saturation of RETR (PPFD~95%~) and maximum RETR (ETR~max~) were then calculated from the curve.
Light responses were measured in eight individuals per species in the lab for sporophytes, and on single individuals in the field for gametophytes. The gametophytes were later identified to species using the DNA barcodes.

@@

Datasets used in this study are available on FigShare (\#\#\#\#\#\#). 
Code used to analyze the data and generate figures and this manuscript are available on GitHub (https://github.com/joelnitta/moorea-filmies).
A Docker image is available to run the code at https://hub.docker.com/r/joelnitta/moorea_filmies.
The \package{targets} package [@Landau2021] was used to automate the workflow.
The \package{ggplot2} [@Wickham2016], \package{ggtree}, [@Yu2017] and \package{patchwork} (https://github.com/thomasp85/patchwork) packages were used to generate the figures.

>>>>

Samples were collected in the field and stored in plastic bags with a small amount of water to keep them fresh during transport to the lab.
For sporophytes, 8 individuals (one individual = single whole frond including a \circa{ }2 cm section of rhizome) were used per treatment, and all individuals for each species came from a single population.
We did not attempt to differentiate genotypes between fronds in species with long-creeping rhizomes, which often form clonal mats; hence, in some cases, individuals may be genetically identical ramets.
All experiments were initiated within 48 h of collection.
Pre-treatment maximum photochemical yield of photosystem II (F~v~/F~m~) [@Kitajima1975] was measured in fresh plants after a 10 min period of dark-adaptation using a portable mini-PAM chlorophyll fluorometer (Walz Gmbh, Effeltrich, Germany).
Any samples with pre-treatment F~v~/F~m~ < 0.4 were excluded from analysis, as typical values of F~v~/F~m~ in healthy plants tend to be \circa{ }0.8 [@Bjorkman1987].
Samples were then transferred to desiccation chambers containing saturated salts at three different desiccation intensities or a control treatment with moist tissues (100 % RH), and water withheld for either a short (2 d) or long (15 d) interval [@Testo2013].
Conditions inside the desiccation chambers were monitored during the experiment using Track-It RH/Temp dataloggers (Monarch Instrument, Amherst, NH) logging every 10 min (2012 field season for species other than *Callistopteris apiifolia*) or Hobo ProV2 dataloggers logging every 5 min (2012 *Callistopteris apiifolia*, 2013, 2014 field seasons).
The desiccation chambers were kept in an air-conditioned room. 
Temperature inside the chambers was mean `mean(filmy_dt_chamber$temp) %>% round(1)` ± SD `r sd(filmy_dt_chamber$temp) %>% round(2)` °C (\figs `r s_figure_num("chamber")`).
Salts used for desiccation and their corresponding mean water potentials and approximate relative humidity and VPD are as follows: LiCl (-282 MPa, 18 % RH, 2.45 kPa), Mg(NO~3~)~2~ (-86 MPa, 58 % RH, 1.25 kPa), and NaCl (-38 MPa, 80 % RH, 0.60 kPa).
Following the desiccation treatment, plants were rewetted by wrapping them in wet tissues using water from a local stream.
Plants were allowed to rehydrate, and F~v~/F~m~ was again measured at 0.5 h, 24 h, and 48 h following rewetting.
Ability to recover from desiccation was quantified by comparing pre- and post-treatment F~v~/F~m~ [@WatkinsJr.2007c].

@@

Rapid light response curves were constructed for each species by measuring photosynthetic yield at gradually increasing levels of photosynthetically active actinic light (400 nm to 700 nm) with the Light Curve function of the mini-PAM portable chlorophyll fluorometer as described by the manufacturer.
Briefly, the maximum yield (F~m~) was first measured in the absence of actinic light.
Next, plants were equilibrated to the actinic light for 30 s, and photosynthetic yield (∆F/F~m~) measured with a 0.8 s saturating pulse.
This was repeated for each photosynthetic photon flux density (PPFD) level, up to ca.
500 µmol·m^-2^·s^-1^.
Response curves were fitted using the equation $y = A(1 - e^{-kx})$, where *y* is relative electron transport rate of photosystem II (RETR), *x* is photosynthetic photon flux density (PPFD), *A* is the asymptote of the curve, and *k* is a slope parameter; outliers at high PPFD likely to distort the curve were discarded [@Proctor2012].
The PPFD at 95 % saturation of RETR (PPFD~95%~) and maximum RETR (ETR~max~) were then calculated from the curve.
Light responses were measured in eight individuals per species in the lab for sporophytes, and on single individuals in the field for gametophytes. The gametophytes were later identified to species using the DNA barcodes.

@@

Datasets used in this study are available on FigShare (https://doi.org/10.6084/m9.figshare.14184572). 
Code used to analyze the data and generate figures and this manuscript are available on GitHub (https://github.com/joelnitta/moorea-filmies).
A Docker image is available to run the code at https://hub.docker.com/r/joelnitta/moorea_filmies.
The \package{targets} package [@Landau2021] was used to automate the workflow.
The \package{ggplot2} [@Wickham2016], \package{ggtree}, [@Yu2017] and \package{patchwork} (https://github.com/thomasp85/patchwork) packages were used to generate the figures.

\*\*\* NOTE TO REVIEWERS: The dataset and code will not be made public until the paper is accepted. While the paper is under review, these links can be used for the dataset (https://figshare.com/s/d6349abf01a3756a5aae) and code (https://www.dropbox.com/sh/h788g1h3sjcqj0j/AACwFWTmL6GxrbLkCfOrXZU9a?dl=0)  \*\*\*
